---
title: "K-means"
output: github_document
---

```{r}
knitr::opts_chunk$set(fig.width=15, fig.height=8)
```

I am going to work with the Iris dataset to demonstate K-means

```{r}
data(iris)

str(iris)
```


```{r}
head(iris)
```

Let's remove the fifth column as it contains the species. We want to frame this exercise as unspuervised learning problem so removing the labels faciliates that. Ideally we will be able to identify a number of groups that correspond to the various species types.

```{r}
iris_raw <- iris[,-5]
```

The pairs R function returns a plot matrix, consisting of scatterplots for each variable-combination of a data frame. The basic R syntax for the pairs command is shown above.

```{r fig.width = 12}
pairs(iris_raw, pch=19, col = adjustcolor(1, 0.4))

```

From the pairing plot above we can see that there are definetely distinct groups. But I can't really guess how many discinct groups in total there might be in the 5 dimensional space.


```{r}

```



```{r}

```


```{r}

```



